\ripple: Differentiable and Hardware-Accelerated Waveforms for Gravitational Wave Data Analysis

### 2024-06-07 src/tex/ms.tex
reply updates

% The coefficients of the original IMRPhenomD implementation are tuned in subsets of parameters instead of all together. 
Since the coefficients for each segment are tuned individually, the correlation between different parameters are ignored, meaning that the provided best-fit solution may not be the global optimum. 
We therefore aim to improve the accuracy of the waveform by jointly fitting all coefficients at once.\footnote{
    For a further breakdown of how the optimization changes across the parameter space, see our accompanying paper~y\citep{Lam:2023oga}.
}

>>>>

% The coefficients of the original IMRPhenomD implementation are tuned in subsets of parameters instead of all together. 
Since the coefficients for each segment are tuned individually, the correlation between different parameters are ignored, meaning that the provided best-fit solution may not be the global optimum. 
We therefore aim to improve the accuracy of the waveform by jointly fitting all coefficients at once.\footnote{
    For a further breakdown of how the optimization changes across the parameter space, see our accompanying paper~\citep{Lam:2023oga}.
}
